---
title: "Homework 1"
output: html_document
---

### Authors :

### Date : `r Sys.time()` 

# Introduction
This is the Geneva Summer School on R for data science! Here we practice on how to make awesome reports with Rmarkdown... Just look at the result...

<iframe width='560' height='315' src='https://www.youtube.com/watch?v=sjkUqyyQ0xU&list=PLFzL8rgahslahw6H569MSEb-Tz8ZVBREp.html' frameborder='0' allowfullscreen></iframe>
# Group Members



## Group Member 1
Some info

## Group Member 2

Some other info


## Group Member 3


Classes Taken | Time of Class
--- | --- |
R-Programming for Data Science | 9 AM
Random Class 1 | 11 AM
Arbitrary Class | 2 PM


# Introduction
1. Information about our group members
2. 

<iframe width='560' height='315' src='https://www.youtube.com/embed/WpE_xMRiCLE' frameborder='0' allowfullscreen></iframe>

# R-Markdown Syntax

```{r}
X = rnorm(100)
mean = mean(X)
median = median(X)
Variance = var(X) 
```

The Mean for the dataset is `r mean`.

The Median for the dataset is `r median`.

The Variance for the dataset is `r Variance`.

```{r}
hist(X)
```


“Vérité dans un temps, erreur dans un autre.”, Charles de Montesquieu


# References

